The controlled choice design and private paternalism in pawnshop borrowing - ONLINE APPENDIX

### 2023-12-02 ECTA submission/OA_ecta.tex
prepare for ecta submission

%  \documentclass[oneside,11pt]{article}

% \input{preamble.tex}
% %%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
% \usepackage{xr}
% \makeatletter
% \newcommand*{\addFileDependency}[1]{
%   \typeout{(#1)}
%   \@addtofilelist{#1}
%   \IfFileExists{#1}{}{\typeout{No file #1.}}
% }
% \makeatother

% \newcommand*{\myexternaldocument}[1]{
%     \externaldocument{#1}
%     \addFileDependency{#1.tex}
%     \addFileDependency{#1.aux}
% }

% %\myexternaldocument{OA}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT
% \begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% APPENDIX 
\setcounter{table}{0}
\setcounter{figure}{0}
\setcounter{section}{0}
\pagenumbering{gobble}

\begin{center}
	\LARGE The limits of self-commitment and private paternalism \\[0.5em]
	\Large{Appendix $-$ For Online Publication} \\[1em]
	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
\end{center}

\appendix
\pagenumbering{arabic}
\renewcommand\thefigure{OA-\arabic{figure}}
\renewcommand\thetable{OA-\arabic{table}}
\renewcommand*{\thepage}{OA - \arabic{page}}
\renewcommand\thesection{Appendix \Alph{section}.}
\renewcommand\thesubsection{\Alph{section}.\arabic{subsection}}

%\renewcommand{\cftparskip}{0em} % NOT NEEDED
\renewcommand\cftsecdotsep{\cftdotsep}
\renewcommand\cftsubsecdotsep{\cftnodots}
\renewcommand{\cftsecnumwidth}{6em}
 \renewcommand{\cftpnumalign}{r}
%\renewcommand{\cftsecleader}{\normalfont\cftdotfill{\cftsecdotsep}}

\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}\hspace{1.8em}}
%\renewcommand{\cftsecpagefont}{20em}
%\renewcommand{\cftfignumwidth}{6em}
%\renewcommand{\cfttabnumwidth}{3.3em}

%\tableofcontents
\etocdepthtag.toc{mtappendix}
\etocsettagdepth{mtchapter}{none}
\etocsettagdepth{mtappendix}{subsection}

\setstretch{0.9}
%\renewcommand\contentsname{} % the empty name

\begingroup
\let\clearpage\relax
%\vspace{-1.5em} % the removed space. Set as appropriate
\tableofcontents
\endgroup

\newpage

\section{Treatment Explanation Materials and Pictures}
\vspace{.2in}

@@

\begin{figure}[H]
     \caption{Contract Terms Summary}
    \label{PaperSlip}
    \begin{center}
    %\begin{subfigure}{0.65\textwidth}
    %\caption{Receipt for client}
     %   \centering
        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
    %\end{subfigure}

    %\vspace{3ex}
    %\begin{subfigure}{0.65\textwidth}
    %\caption{Personal promise signed by client}
     %   \centering
    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
    %\end{subfigure}
    \end{center}
    \scriptsize
        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity). We want to highlight the salience of some items. First the title clearly indicated which contract the client has (arrow 1). Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2). Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month. %The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient. It emphasizes that the client is giving his word, and that the promise is not a legal document.
\end{figure}

\begin{figure}[H]
     \caption{Explanatory Material}
    \label{ExplanatoryMaterial}
    \begin{center}
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
\end{figure}

\cleardoublepage

@@

\begin{figure}[H]
     \caption{Some Pawnshops}
    \label{PawnshopPicture}
    \begin{center}
    \begin{subfigure}{0.405\textwidth}
    \caption{Appraiser/tellers inside a pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
    \end{subfigure}

@@

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
    \end{subfigure}
    \begin{subfigure}{0.415\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

\vspace{.1in}
\begin{figure}[H]
     \caption{Gold buyers next to pawnshops}
    \label{GoldBuyers}
    \begin{center}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
    \end{subfigure}
       \vspace{3ex}

    \end{center}
    \scriptsize
        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

\begin{comment}
\\
\begin{table}[H]
\caption{Number of pawns balance before and after the experiment}
\label{num_pawns_bal}
\begin{center}
\scriptsize{\input{./Tables/num_pawns_bal.tex}}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{num\_pawns\_bal.do}
\end{table}
\end{comment}
%\todo[inline]{removed}

\newpage
\subsection{Survey}   \label{app:survey_data}

\vspace{.2in}

@@

\cleardoublepage

\begin{table}[H]
\caption{Baseline survey questions (translated to English)}
\label{baseline_survey}
\begin{center}
\scriptsize{\input{./Tables/transcribed.tex}}
\end{center}
\scriptsize
Translation of the baseline questionnaire.
\end{table}

\cleardoublepage

\newpage
\subsection{Descriptives consistent with overconfidence}

\vspace{.2in}
\begin{figure}[H]
    \caption{Behavior of borrowers who lost their pawn}
    \label{proxy_naive}
    \begin{center}
    \begin{subfigure}{0.40\textwidth}
        \caption{Elapsed days to first payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
        \caption{Elapsed days to last payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
    \end{subfigure}
        \begin{subfigure}{0.40\textwidth}
        \caption{Payments as \% of loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
    \end{subfigure}
    \end{center}
        \scriptsize 
        This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn. Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment. Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan. This amounts to starting a new loan with the same conditions and same pawn. Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.
      %\textit{Do file: }  \texttt{hist\_den\_default.do}
\end{figure}

\vspace{.1in}
\section{Internal Validity}

\begin{figure}[H]
     \caption{Box-plot across arms}
    \label{boxplot_attrition}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
    \caption{Number of pawns}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Number of borrowers}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms. The solid black line represent the median, while the gray line represent the mean. The dots on top of the box-plot represent an implicit CDF. 
\end{figure}

% \begin{figure}[H]
%      \caption{Number of pawns and borrowers before and after the experiment}
%     \label{line_pawns_before_after}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/after_before_bal.pdf}
%     \scriptsize
%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
% \end{figure}

% \begin{figure}[H]
%      \caption{No discontinuity in the number of pawns before and after experiment}
%     \label{rd_pawns}
%        \begin{center}
%     \begin{subfigure}{0.45\textwidth}
%     \caption{Number of pawns - before}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_before_pawns.pdf}
%     \end{subfigure}
%         \begin{subfigure}{0.45\textwidth}
%     \caption{Number of pawns - after}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_after_pawns.pdf}
%     \end{subfigure}
%      \begin{subfigure}{0.42\textwidth}
%     \caption{Number of borrowers - before}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_before_borr.pdf}
%     \end{subfigure}
%         \begin{subfigure}{0.45\textwidth}
%     \caption{Number of borrowers - after}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_after_borr.pdf}
%     \end{subfigure}
%     \end{center}
%     \scriptsize
%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
% \end{figure}

\begin{table}[H]
\caption{Balance conditional on survey response and question-by-question response rates by treatment arm}
\label{SS_cond_survet}
\begin{center}
\scriptsize{\input{./Tables/SS_cond_survey.tex}}
\end{center}
\scriptsize

Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered at least one question in our baseline survey. Conditional on survey response, loan amount and weekday are balanced across treatment arms. Panel B presents response rates to each individual survey question across treatment arms, along with p-values for the F-test of no difference in response rates across survey arms. This panel uses data for borrowers who pawned on the same day as their survey response.

@@

\begin{landscape}
\begin{table}[H]
\caption{Survey Non-response: TUT estimates for respondents to each survey question.}
\label{TUT_cond_survet}
\begin{center}
\scriptsize{\input{./Tables/tut_cond_survey.tex}}
\end{center}
\scriptsize

Some borrowers did not respond to our survey; others only completed part of the survey.
This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
The top panel uses financial cost as the outcome variable, while the bottom panel uses APR.
Each group is defined by the borrowers who responded to a particular \emph{subset} of the survey questions. 
For example, column (4) computes TUT effects for the subgroup of borrowers who responded to the two questions needed to compute our measure of present bias, while column (8) computes the TUT for the subgroup of borrowers who provided their age.
The bottom row of the table counts the number of borrowers in each category.
TUT estimates are quite stable across sub-groups and generally similar to the full-sample estimates.
Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.
%\textit{Do file: } \texttt{tut_cond_survey.do}
\end{table}
\end{landscape}

\newpage
\section{Main treatment effects: Additional material}

@@

\begin{table}[H]
\caption{Multiple-loans robustness check}
\label{multiple_loans}
\begin{center}
\scriptsize{\input{./Tables/multiple_loans.tex}}
\end{center}
 \scriptsize
 An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.  43\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.  The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure (ITT) \citep{cullen2006effect, abdulkadirouglu2011accountability}.\\

 This table provides robustness for our main results for different ways to handling the multiplicity of loans. Columns 1-4 repeat the main analysis of financial cost and APR using the baseline approach from our main results,i.e. it only considers the first visit, while allowing multiple loans for the same-day. Columns 5-8 considers all loans including dummies for the order of pawns for an individual, essentially making the identification within-order.  Columns 9-12 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns. The core treatment effects are robust to any of these ways of handling repeat pawning.

@@

\begin{figure}[H]
    \caption{Determinants of choice}
    \label{determinants_choose}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
    \end{subfigure}
    \end{center}
      \scriptsize

      The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment. Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm. 
%\textit{Do file: } \texttt{determinants_choice.do}       
\end{figure}

\vspace{.2in}
\begin{figure}[H]
    \caption{Histogram of payments}
    \label{hist_payments}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{Status-quo}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{Forced commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{Choice commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
    \end{subfigure}    
    \end{center}
     \scriptsize
     This figure shows the schedule of payments for each treatment arm. In other words it records the time after the loan origination when the borrower makes a payment toward recovery of the pawn. We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).

@@

\cleardoublepage

@@

\vspace{.2in}

@@

\vspace{.3in}
\begin{table}[H]
\caption{Bounding censoring} 
\label{bounding_censoring}
\begin{center}
\resizebox{0.9\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp.tex}}
}
\end{center}

\end{table}
 \scriptsize 
 Given the censored loans, i.e. loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm. Different panels perform different imputations for the censored loans for all possible combinations for the imputation, and computes the ATE for the same outcomes of Table \ref{main_impact_table}. Panel A, for instance, assumes that all outstanding loans are fully payed. Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the forced commitment arm default. Panel C, on the other hand, is the most optimistic scenario opposite to that of Panel B. Panel D assumes all remaining loans default. The last panel makes the imputation to the censored loans according to the best prediction using a piecewise lasso logit model for default. In concrete, we build two logit models with lasso regularization, depending whether the loan duration is less than 220 days (two cycles) or more than 220 days. For prediction we use the former whenever the last recorded payment was done within 220 days, and the latter otherwise. Both models includes loan characteristics (loan size, branch), and payment behavior (loan duration so far, days to first payment, \% of first payment, \% of payments at 30, 60, 90, and 105 days, and \% of interest payed at 105 days), but the latter model also includes \% of payments at 150, 180, and 210 days. This predictive model achieves an accuracy rate of 92\% both in-sample and out-of-sample.

 Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome.

\begin{figure}[H]
        \caption{Interpolation on bounding censoring}
    \label{interpolation_censoring_imp}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
    \end{subfigure}     
    \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for Default }
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_def_imp.pdf}
    \end{subfigure} 
    \end{center}
     \scriptsize  The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
     This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment. Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}. For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel B) is the worst-case scenario. Thus we can think of this graph as an `interpolation' from the four extreme cases. The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels. We do not include the plot for financial cost, since for any imputation we still have significant results.

@@

\begin{figure}[H]
        \caption{Survival graph}
    \label{survival_graph}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Ended contract}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
   \caption{Recovery}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
    \end{subfigure}     
    \end{center}
     \scriptsize  This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.
     %\textit{Do file: }  \texttt{survival\_graph.do}
\end{figure}

>>>>

\pagenumbering{arabic}
\renewcommand\thefigure{OA-\arabic{figure}}
\renewcommand\thetable{OA-\arabic{table}}
\renewcommand*{\thepage}{OA - \arabic{page}}
\renewcommand\thesection{Appendix \Alph{section}.}
\renewcommand\thesubsection{\Alph{section}.\arabic{subsection}}

\begin{frontmatter}

\title{The controlled choice design and private paternalism in pawnshop borrowing - ONLINE APPENDIX}
\runtitle{The controlled choice design and private paternalism}

\begin{aug}
% use \particle for den|der|de|van|von (only lc!)
% [id=?,addressref=?,corref]{\fnms{}~\snm{}\ead[label=e?]{}\thanksref{}}
%
%% e-mail is mandatory for each author
%
%%% initials in fnms (if any) with spaces
%
\author[id=au1,addressref={add1}]{\fnms{Craig}~\snm{McIntosh}\ead[label=ee1]{ctmcintosh@ucsd.edu}}
\author[id=au2,addressref={add2}]{\fnms{Isaac}~\snm{Meza}\ead[label=ee2]{isaacmezalopez@g.harvard.edu}}
\author[id=au3,addressref={add3}]{\fnms{Joyce}~\snm{Sadka}\ead[label=ee3]{jsadka@itam.mx}}
\author[id=au4,addressref={add4}]{\fnms{Enrique}~\snm{Seira}\ead[label=ee4]{enrique.seira@gmail.com}}
\author[id=au5,addressref={add5}]{\fnms{Francis J.}~\snm{DiTraglia}\ead[label=ee5]{francis.ditraglia@economics.ox.ac.uk}}

% Addresses
\address[id=add1]{%
\orgdiv{Department of Economics}
\orgname{University of California San Diego}}

\address[id=add2]{%
\orgdiv{Department of Economics}
\orgname{Harvard University}}

\address[id=add3]{%
\orgdiv{Department of Economics}
\orgname{Instituto Tecnologico Autonomo de Mexico}}

\address[id=add4]{%
\orgdiv{Department of Economics}
\orgname{Michigan State University}}

\address[id=add5]{%
\orgdiv{Department of Economics}
\orgname{University of Oxford}}
\end{aug}

\end{frontmatter}

\begin{appendix}

\section{Treatment Explanation Materials and Pictures}

@@

\begin{figure}[!htb]
     \caption{Contract Terms Summary}
    \label{PaperSlip}
    \begin{center}
        \includegraphics[width=0.7\textwidth]{Figuras/TicketLenderP.png}
    \end{center}
    \legend{We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity). We want to highlight the salience of some items. First the title clearly indicated which contract the client has (arrow 1). Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2). Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.}
\end{figure}

\begin{figure}[!htb]
     \caption{Explanatory Material}
    \label{ExplanatoryMaterial}
    \begin{center}
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.7\textwidth]{Figuras/micas.pdf}
    \end{subfigure}
    \end{center}
    \legend{ This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.}
\end{figure}

@@

\begin{figure}[!htb]
     \caption{Some Pawnshops}
    \label{PawnshopPicture}
    \begin{center}
    \begin{subfigure}{0.405\textwidth}
    \caption{Appraiser/tellers inside a pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
    \end{subfigure}

@@

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
    \end{subfigure}
    \begin{subfigure}{0.415\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
    \end{subfigure}
    \end{center}
   \legend{ This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
\end{figure}

\begin{figure}[!htb]
     \caption{Gold buyers next to pawnshops}
    \label{GoldBuyers}
    \begin{center}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
    \end{subfigure}
       \vspace{3ex}

    \end{center}
    \legend{  This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
\end{figure}

\subsection{Descriptives consistent with overconfidence}

\vspace{.2in}
\begin{figure}[!htb]
    \caption{Behavior of borrowers who lost their pawn}
    \label{proxy_naive}
    \begin{center}
    \begin{subfigure}{0.40\textwidth}
        \caption{Elapsed days to first payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
        \caption{Elapsed days to last payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
    \end{subfigure}
        \begin{subfigure}{0.40\textwidth}
        \caption{Payments as \% of loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
    \end{subfigure}
    \end{center}
       \legend{ This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn. Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment. Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan. This amounts to starting a new loan with the same conditions and same pawn. Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.}
      %\textit{Do file: }  \texttt{hist\_den\_default.do}
\end{figure}

\section{Internal Validity}

\subsection{Survey}   \label{app:survey_data}

@@

\begin{table}[!htb]
\caption{Baseline survey questions (translated to English)}
\label{baseline_survey}
\begin{center}
\scriptsize{\input{./Tables/transcribed.tex}}
\end{center}
\legend{ Translation of the baseline questionnaire.}
\end{table}

\begin{figure}[!htb]
     \caption{Box-plot across arms}
    \label{boxplot_attrition}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
    \caption{Number of pawns}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Number of borrowers}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
    \end{center}
    \legend{ This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms. The solid black line represent the median, while the gray line represent the mean. The dots on top of the box-plot represent an implicit CDF. }
\end{figure}

\begin{table}[!htb]
\caption{Balance conditional on survey response and question-by-question response rates by treatment arm}
\label{SS_cond_survet}
\begin{center}
\scriptsize{\input{./Tables/SS_cond_survey.tex}}
\end{center}
\legend{ Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered at least one question in our baseline survey. Conditional on survey response, loan amount and weekday are balanced across treatment arms. Panel B presents response rates to each individual survey question across treatment arms, along with p-values for the F-test of no difference in response rates across survey arms. This panel uses data for borrowers who pawned on the same day as their survey response. }

@@

\begin{landscape}
\begin{table}[!htb]
\caption{Survey Non-response: TUT estimates for respondents to each survey question.}
\label{TUT_cond_survet}
\begin{center}
\scriptsize{\input{./Tables/tut_cond_survey.tex}}
\end{center}
\legend{ Some borrowers did not respond to our survey; others only completed part of the survey.
This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
The top panel uses financial cost as the outcome variable, while the bottom panel uses APR.
Each group is defined by the borrowers who responded to a particular \emph{subset} of the survey questions. 
For example, column (4) computes TUT effects for the subgroup of borrowers who responded to the two questions needed to compute our measure of present bias, while column (8) computes the TUT for the subgroup of borrowers who provided their age.
The bottom row of the table counts the number of borrowers in each category.
TUT estimates are quite stable across sub-groups and generally similar to the full-sample estimates.
Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.}
%\textit{Do file: } \texttt{tut_cond_survey.do}
\end{table}
\end{landscape}

\section{Main treatment effects: Additional material}

@@

\begin{table}[!htb]
\caption{Multiple-loans robustness check}
\label{multiple_loans}
\begin{center}
\scriptsize{\input{./Tables/multiple_loans.tex}}
\end{center}
 \legend{ An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.  43\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.  The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure (ITT) \citep{cullen2006effect, abdulkadirouglu2011accountability}.\\
 This table provides robustness for our main results for different ways to handling the multiplicity of loans. Columns 1-4 repeat the main analysis of financial cost and APR using the baseline approach from our main results,i.e. it only considers the first visit, while allowing multiple loans for the same-day. Columns 5-8 considers all loans including dummies for the order of pawns for an individual, essentially making the identification within-order.  Columns 9-12 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns. The core treatment effects are robust to any of these ways of handling repeat pawning.  }

@@

\begin{figure}[!htb]
    \caption{Determinants of choice}
    \label{determinants_choose}
    \begin{center}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
    \end{subfigure}
    \end{center}
      \legend{  The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment. Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm. }
%\textit{Do file: } \texttt{determinants_choice.do}       
\end{figure}

\vspace{.2in}
\begin{figure}[!htb]
    \caption{Histogram of payments}
    \label{hist_payments}
    \begin{center}
    \begin{subfigure}{0.32\textwidth}
        \caption{Status-quo}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
    \end{subfigure}
    \begin{subfigure}{0.32\textwidth}
        \caption{Forced commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
    \end{subfigure}
    \begin{subfigure}{0.32\textwidth}
        \caption{Choice commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
    \end{subfigure}    
    \end{center}
     \legend{ This figure shows the schedule of payments for each treatment arm. In other words it records the time after the loan origination when the borrower makes a payment toward recovery of the pawn. We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).}

@@

@@

@@

\begin{table}[!htb]
\caption{Bounding censoring} 
\label{bounding_censoring}
\begin{center}
\resizebox{0.9\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp.tex}}
}
\end{center}

 \legend{  Given the censored loans, i.e. loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm. Different panels perform different imputations for the censored loans for all possible combinations for the imputation, and computes the ATE for the same outcomes of Table \ref{main_impact_table}. Panel A, for instance, assumes that all outstanding loans are fully payed. Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the forced commitment arm default. Panel C, on the other hand, is the most optimistic scenario opposite to that of Panel B. Panel D assumes all remaining loans default. The last panel makes the imputation to the censored loans according to the best prediction using a piecewise lasso logit model for default. In concrete, we build two logit models with lasso regularization, depending whether the loan duration is less than 220 days (two cycles) or more than 220 days. For prediction we use the former whenever the last recorded payment was done within 220 days, and the latter otherwise. Both models includes loan characteristics (loan size, branch), and payment behavior (loan duration so far, days to first payment, \% of first payment, \% of payments at 30, 60, 90, and 105 days, and \% of interest payed at 105 days), but the latter model also includes \% of payments at 150, 180, and 210 days. This predictive model achieves an accuracy rate of 92\% both in-sample and out-of-sample.
 Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome. }
 \end{table}

\begin{figure}[!htb]
        \caption{Interpolation on bounding censoring}
    \label{interpolation_censoring_imp}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
    \end{subfigure}     
    \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for Default }
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_def_imp.pdf}
    \end{subfigure} 
    \end{center}
     \legend{  The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
     This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment. Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}. For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel B) is the worst-case scenario. Thus we can think of this graph as an `interpolation' from the four extreme cases. The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels. We do not include the plot for financial cost, since for any imputation we still have significant results.}

@@

\begin{figure}[!htb]
        \caption{Survival graph}
    \label{survival_graph}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Ended contract}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
   \caption{Recovery}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
    \end{subfigure}     
    \end{center}
     \legend{  This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.}
     %\textit{Do file: }  \texttt{survival\_graph.do}
\end{figure}
